---
layout: page
title: curriculum vitae
excerpt: My current CV
engine: knitr 
toc: true
toc-location: left
toc-title: curriculum vitae
editor_options: 
  chunk_output_type: console
---

```{css echo=FALSE}

```

```{r, echo = F}
# knitr global options ----
knitr::opts_chunk$set(fig.pos = 'H',
                      echo = F,
                      message = F,
                      warning = F, 
                      dpi = 600,
                      fig.align = "center", 
                      fig.asp = 0.62) # golden ratio
```


## Education - degrees
```{r}

edu <- read.csv("edu.csv") 

names(edu) <- NULL 
n_rows <- nrow(edu)
kableExtra::kable(edu, kable_format = "html", align = c("r", "l")) |> 
  kableExtra::column_spec(1, 
                          width_min = "4cm") |> 
  kableExtra::row_spec(row = 1:n_rows, extra_css = "line-height: 1.2;
                       padding: 10px")
```

## Education - further courses

```{r}
edu_further <- read.csv("Further_edu.csv") 
names(edu_further) <- NULL 
n_rows <- nrow(edu_further)
kableExtra::kable(edu_further, kable_format = "html", align = c("r", "l")) |> 
  kableExtra::column_spec(1, 
                          width_min = "4cm") |> 
  kableExtra::row_spec(row = 1:n_rows, extra_css = "line-height: 1.2;
                       padding: 10px")
```
## Employment

```{r}
empl <- read.csv("employ.csv") 
names(empl) <- NULL 
kableExtra::kable(empl, kable_format = "html", align = c("r", "l")) |> 
  kableExtra::column_spec(1, 
                          width_min = "4cm") |> 
  kableExtra::row_spec(row = 1:10, extra_css = "line-height: 1.2;
                       padding: 10px") |> 
  kableExtra::row_spec(row = c(4,6, 8, 10), bold = TRUE, italic = T, color = "gray")
```


## Teaching 

```{r}
teach <- read.csv("Teach.csv") 
names(teach) <- NULL 

urls <- c("https://www.bne.unibe.ch/unibe/portal/microsites/BNE/content/e497827/e608437/e721277/e955542/pane1150436/e1144780/Abstract_Conclusion_FNE_Gurtner_ger.pdf", 
          "", # data literacy class 
          "https://osf.io/78ct6/") # psy and sust class)

kableExtra::kable(teach, 
                  kable_format = "html", 
                  align = c("r", "l"), 
                  escape = F) |> 
  kableExtra::column_spec(1, 
                          width_min = "4cm") |> 
  kableExtra::row_spec(row = 1:16, 
                       extra_css = "line-height: 1.2;
                       padding: 10px") |> 
  kableExtra::row_spec(1, hline_after = T)
```


## Grants

```{r}

grants <- read.csv("Grants.csv") 
names(grants) <- NULL 
n_row <- nrow(grants)
kableExtra::kable(grants, kable_format = "html",  align = c("l", "l", "r", "r")) |> 
  kableExtra::column_spec(1, 
                          width_min = "3cm") |>
    kableExtra::column_spec(2, 
                          width_min = "3cm") |> 
  kableExtra::row_spec(row = 1:n_row, 
                       extra_css = "line-height: 1.2;
                       padding: 10px") |> 
  kableExtra::row_spec(1, hline_after = T)
```


## Personal competences

```{r}

persComp <- read.csv("persComp.csv") 
names(persComp) <- NULL 
kableExtra::kable(persComp, kable_format = "html") |> 
  kableExtra::column_spec(1, 
                          width_min = "4cm") 
```

## Outreach activities

- Participation in a workshop on attractive sufficiency narratives by the [Community Fund of the Mercator Stiftung](https://www.stiftung-mercator.ch/en/offers/community-fund) and the [One Planet Lab](https://www.one-planet-lab.ch/) (January 2026)
- Co-Moderation of the Swiss Climate Podcast [Treibhaus](https://treibhauspodcast.ch/) (since November 2025)
- Organization of "Lunch Discussions" together with the [ESD](https://bne.unibe.ch/index_eng.html) and the SUB - Lunches open to all members of the University of Bern, with guiding questions around sustainability [[link]](https://bne.unibe.ch/community/lunch_discussion/index_ger.html) (2024, 2026)
- Participation in living library discussion on "Psychology and Transformation: what can they learn from each other?" [Living Library](https://scich.org/en/local-projects/living-library/) (18.09.2024)
- Member of researcher panel in the [„stories for future“ project](https://storiesforfuture.ch/) (since 2024)
- Presentation in the Eco Summer Camp (2024)
- Leader & Producer of Podcast [„Zukunftswerkstatt - Ideas and Pathways to tomorrow“](https://www.podcast.de/podcast/3277597/zukunftswerkstatt-ideen-und-wege-ins-morgen) (German, Aug 2023 - Nov 2024)
- Presentation in the Eco Summer Camp (2023)
- Participation in panel discussion on Sustainability, Environmental Group Belp (2023)
- Franxini Nano talk: [“Yes we can - combat climate change with our brains”](https://www.youtube.com/watch?v=uhaeB4taTZk) (2021)
- Public talk at Quadrat: [“Where can we go with this brain?”](https://www.youtube.com/watch?v=SnURgaTHwEA) (talk in Swissgerman, 2021)
- Proofread “Die Gretchenfrage im 21. Jahrhundert“ by Markus Neuenschwander (2020)
- Proofread [“Black mamba - or the power of imagination“](https://www.herder.de/leben/shop/p6/58389-black-mamba-oder-die-macht-der-imagination-ebook-epub/) by Prof. Fred Mast (2020)



