---
title: "Psychology of Sustainability: What do we need to act?"
runningheader: "Psychology of Sustainability" # only for pdf output
subtitle: "Mondays, 10:15 - 12am, vonRoll B101, [KSL](https://ksl.unibe.ch/KSL/kurzansicht?13&stammNr=475347&semester=FS2023&lfdNr=0),  [ILIAS](https://ilias.unibe.ch/goto_ilias3_unibe_crs_2594060.html)" # only for html output
author: "Lilla Gurtner - lilla.gurtner@unibe.ch"
format:
  html:
    embed-resources: true
editor: visual
theme: lux
bibliography: /Users/gurtnerlilla/UniBe/Doktorat/RQA/maintenance/Full_Analysis_and_Paper/src/library.bib
toc: true
---

```{=html}
<!---

INCLUDE NEXT TIME
März 2023: Talk about finite and infinite games: https://www.youtube.com/watch?v=qdIP6HilbWE, https://www.youtube.com/watch?v=r6ME0_iXr4M

Include "Costly distractions" Hagmann2023 into curriculum

August 2023: https://80000hours.org/after-hours-podcast/episodes/hannah-boettcher-mental-health-challenges/ 80k after hour podcast about mental health isses of effective altruists. Also: should I have kids in this world? Self-compassion, perfectionism

Nov23: Jackson2005: review on consumption behaviour, check it out!

Dez23: rest is resistence: https://www.youtube.com/watch?v=zUe5EAJkYfA

--->
```
```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

```{r setup_mine, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Course description

Scientific evidence is conclusive: in order to mitigate climate change, we need to act now, as individuals and as entire societies. Despite ambitious goals, actions to mitigate climate change have not yet yielded the aspired effects. This proseminar is dedicated to understanding the underlying psychological reasons for these shortcomings. We begin at the individual level focusing on cognitive biases, motivated reasoning and systems thinking, but we also discuss consumer decisions, and the role of emotions in climate change. Over the course of the semester, we will also address interactions between individuals (contagious behaviour, imitation and learning from others) and within larger groups, focusing on social cognition and group dynamics to better understand how individuals behave as part of a group.

The key idea is that our brain is a biological, evolved cognitive tool with its particular strengths (empathy, sense of fairness, long-term thinking) and weaknesses (often not rational, challenged by complexity and non-linear relationships). When we understand these strengths and weaknesses better, we are in a better position to engage as many people as possible in the mitigation of climate change. This is particularly important given that the "human factor" is often neglected in climate change mitigation strategies, which can for example lead to resistance in uptake of sustainable habits or policies. Understanding both the capacity and limits of our cognitive and motivational capabilities will put students from all disciplines into a position to tune their discipline-specific contribution to the reality of individuals in a society.

The sessions will be structured as follows: First, we briefly discuss the "basic reading", which is done by half of the class alternating every week. The part of the class that read the text will explain the most important concepts to the other half of students. The explications will be collected and made available on ILIAS by the students in charge of the session. Next, in the presentation part, the in-charge-students will present and discuss their paper. Finally, in the [Activist Part], we will address changes in our own lives, on the individual level and beyond. Active participation in this part is encouraged but not mandatory.\
Exceptions from this structure are the first and last session. Here, the basic reading material must be read by all students. In the first session, we will assign the presentation topics to groups, and in the last session we will have a extended discussion of the content of the proseminar.

# How to prepare for class

The "basic reading" paper is read by half of the class (Group A and B), alternating every week. If it is your turn, read the "basic reading" and be prepared to explain it's most important points to others. It is also legitimate to mention, which parts you did not understand.

The presentation groups are in charge of their individual sessions. They have to:

-   Read the "basic reading"

-   Present and discuss the presentation paper(s) (as a group)

-   Visit the "further reading" resources if applicable

-   Take notes in the first part of the session and prepare a summary of the "basic reading" (as a group). This should be uploaded on ILIAS for your fellow students.

-   After you gave your presentation, write a reaction paper (max 1 A4 page) in which you reflect on the paper you presented.

THE REACTION PAPER is at most one A4 page long and typically consists of a first part, in which you briefly(!) summarize the presented paper, and a second part in which you elaborate on your criticisms, applications, connections of the content. But it can also be of other forms, be creative, it will not be graded! I will provide feedback on your writing, so you can make this an opportunity to practice scientific writing. Please see the [Scientific Writing] section for more information about how to write. Every student writes their own reaction paper, it can be in English or German. *It has to be handed in one week after your presentation. If you miss this deadline, you cannot take the exam!*

THE PRESENTATION should be only 15, maximally 20 min long. This is not much time and you will not be able to present everything you read. This is sometimes a challenge and is part of your learning process. Stick to the most important points for the scope of the proseminar. In the week before it is due, discuss your presentation briefly with me. You are allowed to use any presentation software you like. Again, this will not be graded, so you can be creative. Please put sources on your slides (for pictures and scientific papers etc) and please spare your audience of [death by powerpoint](https://www.youtube.com/watch?v=Iwpi1Lm6dFo)!

# Scientific Writing

Scientific writing is a craft and can be learned by doing it. The reaction paper is intended to give you an opportunity to practice this and get feedback without translating to a grade.

There are some common mistakes that you can avoid:

-   Usually, each paragraph of a (scientific) text has a single topic. This topic is introduced with a topical sentence. For Example: "There are two mayor flaws in the approach from...", "This theory makes an important contribution to understanding of...", "One approach to apply the concept comes from...". Topical sentences prepare your readership for the content of the next paragraph and they are important for the macro structure of your text.

-   Language-wise it is important to be concise and concrete. For example, do not only state that something is important, but tell your readers *why* it is important; do not only say that more research is needed, but explain *what* exactly should be researched and why the results would be important. Also avoid phrases that weaken your statements, such as "This is a little bit questionable". Avoid vague terms such as "somehow", "or so", "maybe", "a bit", if you do not really need them. Think about if you really want to use "can" or "could" rather than "do", such as in "The effects *can* imply that..."

-   When you make comparisons, make sure that both things that are compared are mentioned. For Example: "The method of ... is better. This method uses..." Here, it is not clear, to what this method is compared.

-   In formal written English, you use "it is" and "do not", instead of "it's" and "don't"

-   The university has a very good [writing couneling](https://www.ub.unibe.ch/service/kurse_und_beratung/schreibberatung/index_ger.html#pane1135463) that is free for all students. Don't hesitate to make use of it!

-   There are many online resources on scientific writing, for example the [webpage of Wendy Laura Belcher](https://wendybelcher.com/writing-advice/) has some solid first advice. Also check out this [video by Steven Pinker](https://www.youtube.com/watch?v=OV5J6BfToSw) on why so much writing is so bad and how to change that.

# Activist Part

In the activist part, we will be addressing changes in our own life. We will begin at the individual level and reflect upon our own consumer behavior. The aim is to identify one or two behavioral changes with the highest impact on the climate and the best long-term probability of maintaining the new behavior. Next, we will move on to more social parts of our lives. Which aspects in the daily lives we share with others can we influence? How can we talk to people about the climate crisis to promote change? In the last third of the semester, we will collectively address one aspect on a more institutional level. In general, active participation is encouraged but not mandatory.

# Personal Resources

Climate change can be a personal challenge on many levels. Here you find some resources that might help you.

-   Daniella Nosetti from [Psychologists for Future](https://www.psychologistsforfuture.org/mitarbeit/) has been so kind as to share her slides from a workshop on how to talk about climate change with significant others. The slides (German only) are in the ILIAS-folder "personal resources".

-   [Podcast about having difficult climate discussions with people you like](https://gimletmedia.com/shows/howtosaveaplanet/z3hog9o/trying-to-talk-to-family-about-climate), 35 min

-   Handout "Digital Mindfullness" by Malte Klar, also from Psychologists for Future, with ideas about more healthy media usage is in the ILIAS-folder "personal resources".

-   Lectures by Malte Klar on handling emotions and the climate crisis in [English (45 min)](https://www.youtube.com/watch?v=f-U_dVdXr1s) or [German (31 min)](https://www.youtube.com/watch?v=g4PJC1BIeTQ)

-   [29k](https://29k.org/) is a free mental health and inner development app based on the [inner development goals](https://www.innerdevelopmentgoals.org/)

-   [The way out is in:](https://plumvillage.org/podcasts/the-way-out-is-in/) Zen-Buddhist podcast on personal transformation.

# Learning Goals

You will get a first understanding of the cognitive underpinnings of our reasoning and behavior (both as individuals and as a group), and we will discuss how we can harness these underpinnings to promote change. You will also improve your discursive skills by presenting a scientific paper, practicing challenging conversations in class and remotely, and by (hopefully) having these discussions with real people outside the classroom.

# Grading and Exam

There will be an exam with open questions (and probably some multiple choice questions). To be able to take the exam, handing in the reaction paper on time is mandatory. The text and the presentation will not be graded, but I will give feedback on both.

The proseminar is pass-or-fail.

# Sessions

### 1. Organization and Introduction (20.2.2023)

::: panel-tabset
#### Basic reading - today mandatory for everyone!

-   [Check your worldview: does it correspond to the evidence?](https://upgrader.gapminder.org/t/sdg-world-un-goals/) (10 min)

-   Download the [crancy uncle app](https://crankyuncle.com/), please use our group-code: UNIBEPSYCH (it's case sensitive). Time to train your reasoning skills!

#### Further reading

-   Career advice: Pragmatic and focused on the long-term impact of your work: [web-page](https://80000hours.org/make-a-difference-with-your-career/), [or as a podcast](https://80000hours.org/podcast/episodes/ben-todd-key-ideas-of-80000hours/)

-   The 7 dragons of inaction: @Gifford2018 (an answer to these dragons will be presented in the session on motivated reasoning, @Atkinson2021)
:::

### 2. Cognitive Biases (27.2.2023)

::: panel-tabset
#### Basic reading - Group A - K

-   @Goldstein2011, Chapter 13, p. 393 - 404,

#### Presentation

-   @Goldstein2011, p. 422-424 and @Evans2013

#### Further resources

-   Heuristics and biases: @Tversky1974

-   Cognitive dissonance: @Festinger1959

-   [Podcast on thinking](https://www.bbc.co.uk/programmes/m0011lt1) with Stephen Pinker

-   [Spurious correlations](https://tylervigen.com/spurious-correlations)\
:::

### 3. Short- and long-term thinking (6.3.2023)

::: panel-tabset
#### Basic reading - Group L - Z

-   Roman Krznaric: [six ways to think long term](https://longnow.org/ideas/02020/07/20/six-ways-to-think-long-term-a-cognitive-toolkit-for-good-ancestors/)

#### Presentation

-   @Princen2009 biological and psychological evidence for long-term thinking
:::

### 4. Systems Thinking I (13.3.2023)

::: panel-tabset
#### Basic reading - Group A - K

-   @Meadows2018, Chapter 1: The Basics (p. 11 - 34)

#### Presentation

-   @Meadows2018, Chapter 4: Why systems surprise us (p.86 - 110)

#### Further resources

-   Donella Meadows lecture from 1999: [part 1](https://www.youtube.com/watch?v=HMmChiLZZHg), [part 2](https://www.youtube.com/watch?v=HuIoego-xVc), [part 3](https://www.youtube.com/watch?v=j-k5oSlgIbA), [part 4](https://www.youtube.com/watch?v=d9Lfp8SQ6rc)
:::

### 5. Systems Thinking II (20.3.2023)

::: panel-tabset
#### Basic reading - Group L - Z

-   @Meadows2018, Chapter 5: System traps and opportunities (p. 111 - 141)

#### Presentation

-   @Meadows2018, Chapter 6: Leverage points - Places to intervene in a system (p. 145 - 165)
:::

### 6. Systems Thinking III (27.3.2023)

::: panel-tabset
#### Basic reading - Group A - K

-   An intervention based on systems thinking: @Petersen2018

#### Presentation

-   Climate Action Simulation: @Rooney-Varga2020
:::

### 7. Emotions and Climate Change (3.4.2023)

::: panel-tabset
#### Basic reading - Group L - Z

-   @Chapman2017: Emotion in climate change communication

#### Presentation

-   @Hamann2016de (German) or @Hamann2016en (English), Chapter 7, p. 80

#### Further resources

-   [Lecture on emotions and climate change in the (US) media coverage](https://www.youtube.com/watch?v=DGlU1-JyIbM)

-   How we unite social norms (of being eco-friendly) and our own (mis)behaviour: @Sapiains2015
:::

### Easter Vacation (10.4.2023)

[See what citizen action fits you best](https://www.handabdruck.eu/handabdruck-test)

If you have time, watch:

Julia Steinberger [The importance of activism](https://www.youtube.com/watch?v=2973tOyZ-TA), 45 min

John Robinson [Normalizing Sustainability: beyond behaviour change](https://www.youtube.com/watch?v=wb6KmK3jULA), 43 min

Kate Raworth: Doughnuts economics [@Raworth2017] applied to [the development of cities](https://www.youtube.com/watch?v=batkd7l9Ev0), 38min

Esther Duflo [On government, economics and trust](https://www.youtube.com/watch?v=y-QWSKDj9y8), 82 min

Calling Bullshit - the art of skepticism in a data-driven world: [video lectures](https://www.youtube.com/watch?v=A2OtU5vlR0k&list=PLPnZfvKID1Sje5jWxt-4CSZD7bUI4gSPS) [or as a book](https://www.callingbullshit.org/)

### 8. Motivated reasoning (17.4.2023)

::: panel-tabset
#### Basic reading- Group A - K

-   @Bayes2021 motivated reasoning and climate change

#### Presentation

-   @Atkinson2021: challenging the idea that humans are not designed to solve climate change

-   @Kahan2012: The polarizing impact of science literacy and numeracy on perceived climate change risks

#### Further resources

-   @Kunda1990: the case for motivated reasoning

-   @Lewandowsky2016: motivated rejection of science
:::

### 9. Consumer decisions (24.4.2025)

::: panel-tabset
#### Basic reading - Group L - Z

-   @Verplanken2021: Habits and climate change

#### Presentation

-   @Spangenberg2019: sufficiency and consumer behaviour: from theory to policy

#### Further resources

-   [What has the oil industry to do with your $CO_2$-Footprint? (article in German)](https://perspective-daily.de/article/2001-wer-wirklich-davon-profitiert-wenn-du-ueber-deinen-co2-fussabdruck-nachdenkst/I8OTg7pB)

-   @Mattioli2020: The political economy of car dependence or why it is hard to ditch the car.

-   @Byerly2018: review article on which nudge works when
:::

### 10. Social Learning and Cognition (1.5.2023)

::: panel-tabset
#### Basic reading - Group A - K

-   @Mackay2021: Social identity approach and climate change

#### Presentation

-   @Masson2021: Social identity can motivate climate mitigation behavior

#### Further resources

-   @Hewstone2002: Intergroup bias
:::

### 11. Fairness (8.5.2023)

::: panel-tabset
#### Basic reading - Group L - Z

-   @Jensen2014: Emergence of social norms

#### Presentation

-   @Henrich2006 Costly punishment across human societies

#### Further ressources

-   @VanLange2013: The psychology of social dilemmas: a review
:::

### 12. Social change and minority influence (15.5.2023)

::: panel-tabset
#### Basic reading - Group A - K

-   @Asch1951 Influence of majorities and minorities

#### Presentation

-   @Otto2020: Social tipping dynamics for stabilizing Earth's climate by 2050

#### Further resources

-   Podcast with Cass Sunstein: [how change happens](https://80000hours.org/podcast/episodes/cass-sunstein-how-change-happens/), 105 min

-   @Winkelmann2022 Social tipping points
:::

### 13. Well being and basic human needs (22.5.2023)

::: panel-tabset
#### Basic reading - Group L - Z

-   @Raworth2017 Doughnut economics

#### Presentation

-   @Millward-Hopkins2020: A global scenario of well being within limits

#### Further resources

-   Living well within Limits: [LiLi project overview and call for activism](https://lili.leeds.ac.uk/)

-   Julia Steinberger [Innovation Pathways](https://www.youtube.com/watch?v=Z1VHW3X90-U)
:::

### 14. Discourses of climate delay (29.5.2023)

::: panel-tabset
#### Basic reading - today mandatory for everyone!

-   @Lamb2020: Discourses of climate delay

#### Presentation

-   Group-discussion about how we can use what we learned in the proseminar to counter some of these discourses
:::

### Exam (12.6.2023)

10:15-12am, vonRoll, B101

## References

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
